Geometric variational problems

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
Update broaderimpacts.tex
Intellectual merit

\section{Intellectual Merit}
A central theme of the project is the mathematical development and
analysis of the physical model for interaction between many amphiphilic
particles. The model formulates the interaction potential through a
screened Laplace equation boundary value problem possessing the physical
properties like non-additivity and decay of realistic hydrophobic
attraction. Colloidal systems collectively self-assemble into bilayer
morphologies, and we analyze the elastic properties of these amphiphilic
particle ensembles. This allows us to interpret the Helfrich free energy
in terms of hydrophobic interactions and specific molecular
characteristics. We extend the capabilities of the boundary integral
equation and time stepping methods to stably perform large particle
number simulations in three dimensions. Results from these computations
will be used to compare collective amphiphilic against experiments and
to study the optimal design of three-dimensional functional materials.

>>>>

\section{Intellectual Merit}
The purpose of this research is to reach interesting physical phenomena with 
less computational cost than molecular dynamics, and account for more general
features that continuum theory misses. The main ingredient is defining a 
nonlocal interaction through the solution of an elliptic boundary value problem
that has the phenomenological characteristics of long-range hydrophobic
attraction. It turns out that this minimal model gives rise to rich phenomena
for Janus particle aggregates and correctly predicts elastic properties of bilayer. 
The technical research tasks includes quantifying collective properties of 
amphiphilic ensembles, mathematical analysis of continuum elastic energies, 
efficient, high-order numerical algorithms for large-scale simulations, and 
incorporating external fields such as electric charge. Lastly, the proposal 
extends the results using three-dimensional boundary integral formulations.

%A central theme of the project is the mathematical development and
%analysis of the physical model for interaction between many amphiphilic
%particles. The model formulates the interaction potential through a
%screened Laplace equation boundary value problem possessing the physical
%properties like non-additivity and decay of realistic hydrophobic
%attraction. Colloidal systems collectively self-assemble into bilayer
%morphologies, and we analyze the elastic properties of these amphiphilic
%particle ensembles. This allows us to interpret the Helfrich free energy
%in terms of hydrophobic interactions and specific molecular
%characteristics. We extend the capabilities of the boundary integral
%equation and time stepping methods to stably perform large particle
%number simulations in three dimensions. Results from these computations
%will be used to compare collective amphiphilic against experiments and
%to study the optimal design of three-dimensional functional materials.
